---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# modeldatatoo

<!-- badges: start -->
[![R-CMD-check](https://github.com/tidymodels/modeldatatoo/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tidymodels/modeldatatoo/actions/workflows/R-CMD-check.yaml)
[![CRAN status](http://www.r-pkg.org/badges/version/modeldatatoo)](https://CRAN.R-project.org/package=modeldatatoo)
[![Downloads](http://cranlogs.r-pkg.org/badges/modeldatatoo)](https://CRAN.R-project.org/package=modeldatatoo)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

modeldatatoo contains more data sets used in documentation and testing for tidymodels packages. The package also contains a suite of simulation functions for classification and regression data. This is extension to the [modeldata](https://modeldata.tidymodels.org/) package.

## Installation

You can install the released version of modeldatatoo from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("modeldatatoo")
```

You can install the development version of modeldatatoo from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("tidymodels/modeldatatoo")
```

## Example

All the data sets in this package can be accessed by functions which are prefixed with `data_`, and you call them like functions

```{r}
library(modeldatatoo)
data_elevators()
```

The [pins](https://pins.rstudio.com/) package is used under the hood to read, download, and cache the data.
